Finiteness in Cubical Type Theory

### 2020-06-06 sections/topos.tex
countdown dection

\chapter{Topos} \label{topos}
In this section we will prove that decidable Kuratowski finite types form a
\(\Pi\)-pretopos.
Along the way we will provide closure proofs for a number of the other
finiteness predicates.
As we saw in theorem~\ref{cardinal-kuratowski}, decidable Kuratowski finite
types are equivalent to cardinal finite types, so we will work with the latter
from now on.
Our first task is to show that cardinal finite types are closed under several
operations.
\section{Closure}
For the first three closure proofs, we only consider split enumerability:
as it is the strongest of the finiteness predicates, we can derive the other
closure proofs from it.

% \begin{lemma}
%   \(\bot\), \(\top\), and \(\mathbf{Bool}\) are split enumerable.
% \end{lemma}
% \begin{lemma} \label{split-enum-sigma}
%   Split enumerability is closed under \(\Sigma\).
%   \begin{equation}
%     \frac{
%       \mathcal{E}!(A) \; \; \; \Pi(x : A) , \mathcal{E}!(U(x))
%     }{
%       \mathcal{E}!(\Sigma(x : A) , U(x))
%     }
%   \end{equation}
% \end{lemma}
% From this we can derive split enumerability of non-dependent sums and products,
% as both are definable in terms of \(\Sigma\).

>>>>

\chapter{Topos} \label{topos}
In this section we will examine the categorical interpretation of finite sets.
In particular, we will prove that decidable Kuratowski finite types form a
\(\Pi\)-pretopos.
A lot of the work for this proof has been done already: in
Theorem~\ref{cardinal-kuratowski} we saw that Kuratowski finite types were
equivalent to Cardinally finite types.
We will use the latter definition implementation-wise from now on, as it is
slightly easier to work with: CuTT's transport means we can do this without loss
of generality.

\section{Categories in HoTT}
\section{Closure and the Category of Sets}
\section{The Absence of the Subobject Classifier}

\section{Closure}
For the first three closure proofs, we only consider split enumerability:
as it is the strongest of the finiteness predicates, we can derive the other
closure proofs from it.
